Gas-Efficient Parameter Verification for Blockchain Smart Contracts Using Off-Chain Validators

### 2024-10-08 papers/assertion-contract/fc2025/paper.tex
major revise

\lstdefinelanguage{solidity}{
  backgroundcolor=\color{pink!20},
  keywords={contract, function, public, int},
  keywordstyle=\bfseries\color{blue},
  commentstyle=\itshape\color{green!40!black},
  basicstyle=\ttfamily,
  morecomment=[l]{//},
  morecomment=[s]{/*}{*/},
  morestring=[b]",
  sensitive=true
}
\begin{document}
%
\title{Contribution Title}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Thi Thu Ha Doan\orcidID{0000-0001-7524-4497}\and Peter Thiemann\orcidID{0000-0002-9000-1239}}
%
\authorrunning{Ha Doan, P. Thiemann}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of Freiburg, Germany \\
  \email{\{doanha,thiemann\}@informatik.uni-freiburg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
In certain blockchain scenarios, verifying the properties of parameters may require significant gas costs or be infeasible due to gas limits. This study proposes a distributed verification protocol to address these challenges. The core concept involves offloading the verification process to validators, who attempt to find counterexamples or proofs off-chain. If a counterexample is discovered, it can be submitted for re-verification on-chain. If validated, the parameter is discarded; otherwise, the correctness of the parameter is guaranteed through a proof-of-work incentive mechanism, encouraging validators to participate in the distributed verification process. To implement these ideas, we propose a practical model that also tackles potential security concerns. We developed a prototype of the protocol and conducted a cost analysis, demonstrating its gas efficiency and practical utility.
\keywords{blockchain, off-chain verification, gas optimization, proof-of-work, distributed verification}
\end{abstract}
%
%
%
\section{Introduction}
\label{sec:introduction}
\lstset{language=solidity}
A smart contract is a critical component of blockchain technology, with applications ranging from simple tasks like auctions to more complex systems such as decentralized markets. However, broader adoption of smart contracts faces challenges, with gas costs being among the most significant. Every computation performed by a smart contract on the blockchain incurs a cost, as each unit of computation and storage consumed by an algorithm must be paid for due to the burden it places on the system.

@@

\begin{lstlisting}[numbers=none]
contract Sorted {
  function find (int[100] a, int v) public {
    // assume a is sorted
  }
}
\end{lstlisting}
The explicit assertion would be:
\begin{gather*}\label{}
  (\forall k) (0\leq k <99) \Rightarrow a[k] \leq a[k+1]
\end{gather*}
This check can be performed in \(O(1)\) time, but the associated constant factor makes it costly.

@@

The paper is structured as follows: The next section defines the parameter verification problems and presents use cases. Section \ref{sec:offchain-distributed-verification-approach} proposes the novel approach, while Section \ref{sec:practical-model} introduces its practical model. Section \ref{sec:gas-cost-analysis} analyzes the gas costs, comparing our proposed approach with the on-chain method. Section \ref{sec:prototype-implementation} details the prototype implementation. Section \ref{sec:related-work} discusses related work, and Section \ref{sec:concludes} concludes the paper.
\section{Parameter Assertion Verification On-chain}
\label{sec:parameter-assertion-verification-onchain}
Our work focuses on parameters that are computationally expensive to verify on-chain. Specifically, we address cases where verifying a parameter assertion requires loops within the contract and the assertion can be formalized using universal or existential quantifiers.
\subsection{Parameter Assertion Formalization}
\paragraph{Universal Quantifier Formalization}
An assertion can be formalized using the universal quantifier as follows:
\begin{gather}
  \label{eq:1}
  \forall a \in A. \, P(a)
\end{gather}
This formula can be extended to assertions over multiple domains as:
\begin{gather}
  \label{eq:2}
  \forall a \in A, \, \forall b \in B, \, \dots \, P(a, b, \dots)
\end{gather}
\paragraph{Existential Quantifier Formalization}
In cases where an assertion involves the existence of an element, it can be formalized using existential quantifiers as follows:
\begin{gather}
  \label{eq:3}
  \exists a \in A. \, P(a)
\end{gather}
This formula can also be extended to assertions over multiple domains:
\begin{gather}
  \label{eq:4}
  \exists a \in A, \, \exists b \in B, \, \dots \, P(a, b, \dots)
\end{gather}
\subsection{On-chain Verification}
Verifying these assertions on-chain requires iterating over the domain \(A\) within the contract. For the fomulas \ref{eq:5}, the verification fomulas is as follows.
\begin{gather}
  \label{eq:5}
  \bigwedge_{a \in A} P(a)
\end{gather}
For multiple domains, the verification process becomes:
\begin{gather}
  \label{eq:6}
  \bigwedge_{a \in A, b \in B, \dots} \dots P(a, b, \dots)
\end{gather}
Verifying these assertions in  the existential quantifier formalization requires iterating over the domain \(A\) until finding an element \(a\) that satisfies the predicate:
\begin{gather}
  \label{eq:7}
  \bigvee_{a \in A} P(a)
\end{gather}

@@

\subsubsection{Numbers}

@@

\subsubsection{Booleans}

@@

\subsubsection{Strings}

@@

\subsubsection{Bytes}

@@

\subsubsection{Arrays (or Lists)}

@@

\subsubsection{Sets}

@@

To determine the number of seeds needed based on the expected probability of detecting a problem, we define \( p \) as the expected probability of finding at least one counterexample. 
\begin{itemize}
    \item The probability of a single seed failing to find a counterexample is \( \frac{n-1}{n} \).
    \item The probability of all \( m \) seeds failing is \( \left( \frac{n-1}{n} \right)^m \).
    \item Thus, the probability of at least one seed finding a counterexample is:
\begin{gather*}
  p = 1 - \left( \frac{n-1}{n} \right)^m
\end{gather*}
\end{itemize}
Rearranging this gives:
\begin{gather*}
\left( \frac{n-1}{n} \right)^m = 1 - p
\end{gather*}
Taking the natural logarithm:
\begin{gather*}
m \ln\left( \frac{n-1}{n} \right) = \ln(1 - p)
\end{gather*}
Solving for \( m \):
\begin{gather}
\label{eq:12}
m = \frac{\ln(1 - p)}{\ln\left( \frac{n-1}{n} \right)}
\end{gather}

@@

\begin{enumerate}
\item Denial-of-service (DoS) attacks: The system is susceptible to DoS attacks, where a caller inundates the system with numerous invalid parameters, causing congestion and hindering its operation.
\item Front-running attacks: The system is vulnerable to front-running attacks, where an attacker closely monitors the mempool to intercept a seed representing a counterexample or a computation proof, subsequently stealing the reward.
\item Caller exploitation: A caller might exploit the system by running the negation check privately to (1) identify the reward before submitting the parameter on-chain, thereby swiftly claiming the reward ahead of the other validators, (2) fake the compuatation proofs before a counterexample can be found by other validators.
\item Reward manipulation: For a system that allows multiple rewards. A validator may attempt to manipulate the reward system by resubmitting counterexamples or computation proofs multiple times to multiply their rewards.
\end{enumerate}
\subsection{Overview architect}
This section presents a practical model that unifies theoretical principles and addresses the previously mentioned security concerns. The architectural design of this model is depicted in Figure \ref{fig.architect}.  
\subsubsection{Main compoments.} The model consists of two main entities: the on-chain assertion contract and the off-chain validator program.
\paragraph{On-chain assertion contract.}
While additional functions may exist, the assertion contract must encompass the following two essential functions:
\begin{itemize}
\item The \( submit\_parameter \) function: Callers utilize this function to submit their parameters for validation. %Subsequently, the parameter is distributedly verified by validators.
\item  The \( claim\_reward \) function: This function accepts a seed (or may some others) as inputs, yielding a result indicating whether the computation from the seed results in a counterexample, a reward computation, or a non-reward computation.
\end{itemize}
\paragraph{Off-chain validator program.}
Since the off-chain program runs off-chain, it can be implemented according to the validator's preferences. However, the crucial point is that the off-chain contract must use the exact same \( claim\_reward \) function when attempting to find a counterexample or a computation proof. Additionally, it should support a function that assists the validator in finding a seed to earn a reward.
\paragraph{Storage.}
When a parameter is submitted for verification, the following information should be stored:
\begin{itemize}
\item Parameter: this includes the parameter itself. In cases where storing the parameter on-chain is impractical because of its size, it could be possible to store only its hash. Despite this, the hash remains sufficient for validation.
\item Timestamp: this indicates the approximate time when the parameter was submitted.
\end{itemize}
\begin{figure}
\centering
\includegraphics[scale=.8]{assertion}
\caption{The architecture of the practical model}
\label{fig.architect}
\end{figure}

\subsubsection{Deploying and managing on/off-chain contracts.}
On/off-chain contracts are provided and managed by their respective owners. The owner deploys the assertion contract on the blockchain while storing the validator program off the blockchain, thereby ensuring its accessibility to the validators. There are two ways to making these contracts available to validators.
\begin{itemize}
\item The owner stores the codes on a repository accessible to validators, or upon request, provide them directly to validators.
\item The owner broadcards the contracts to the network using messaging systems such as Waku in Ethereum. In this scenario, the interested validators are responsible for locally storing off-chain code.
\end{itemize}
\subsubsection{Submitting a parameter.} 
Before a parameter can be utilized in the actual work function or contract, a caller must initially submit it via the submit-parameter function in the on-chain assertion contract.

Upon the submission of a parameter, an event can be emitted, allowing validators to receive updates by monitoring the blockchain for the parameter submission event. Additionally, the caller may choose to broadcast their parameter to all validators via a messaging system when submitting it online.
\subsubsection{Off-chain verification}
After a parameter is submitted and stored on-chain, a validator can commence the verification process. To assess the validity of a parameter, each validator independently executes the off-chain validation program.

A validator may attempt to try multiple times with different random seeds in order to find either a counterexample or a computational proof. A function called find-seed could be implemented, which in turn calls the claim-reward function to locate a seed.

All events such as parameter submissions, the discovery of a counterexample, or the presentation of computational proofs can be broadcasted to the network using event emission. Validators can monitor these events to stay updated on the verification status in real-time. 
\subsubsection{Calling a work function}
A work function can indeed be encapsulated either as a private function in the assertion contract or implemented in another contract. In this process, a caller initiates the submission of a parameter for verification by invoking the submit-parameter function within the on-chain assertion contract. Upon successful verification of the parameter, a work contract can be triggered to execute the designated task, operating under the assumption of the parameter's validity.

The invocation of the work function or contract is carried out by the on-chain validation contract or a caller. This call is subject to specific requirements being met, ensuring that the task is executed only when the verification process has been successfully completed and the parameter is deemed valid, such as a certain amount of time having passed, no counterexample being found, and receiving enough computation proofs. If all conditions are met, the actual work is executed, and in some application, the record of the parameter may be deleted from memory to free up storage.
\subsection{Security Features}
\subsubsection{DoS attacks}
When submitting the parameter, the caller need to send a deposit stake in the form of a native token. This stake is claimed by a validator who finds a counterexample. This stake returns to the caller when the parameter is verified.

The deposit serves as a deterrent, as in the event of an invalid parameter, the deposit may be forfeited to prevent callers from submitting such parameters solving the DoS attack security risk. 
\subsubsection{Front-running attacks}
While a random number $r$ alone as a seed is sufficient to indicate the associated element $a$ in the domain $A$, to prevent the front-running attack, we enhance the randomness of the seed by combining a random number with the validator's address to calculate the seed. In deeds, the validator's address is converted to numerical values and use these numbers in combination with a random number to compute the seed.

Let's denote the validator's address by $addr$: \(\quad \text{addr} \in \text{Addresses}\)

The address is converted to numerical values.
\begin{equation}
\text{addr\_num} = \text{init256}(\text{addr})
\end{equation}

This combination adds an extra level of security. So even watching the mempool and get the random number, a malicious validators cannot use the same random number $r$  because the combination with their address will not produce the same seed $s$.
\subsubsection{Caller exploitation attack}
A caller may run the validator program for their parameters before submitting it on-chain and the quickly submit it right after submitting the parameters to either get the computation reward or prove the valid of their parameters before  counterexamples found by other validators.

To prevent this security sisk, the block timestamps indicating when the parameter is submitted on the chain is included to calculate the seed. The seed is enhanced by combining a random number with the validator's address and timestamps.

 Let's denote the timestamp by \( t \in \text{Timestamps}\). The seed $s$ is computed by combining these numerical values.
\begin{equation}
s = \text{hash}(r, \text{addr\_num}, t)
\end{equation}
where \(\text{hash}\) is a hash function that takes the three numerical values and returns a numerical value \( s \).
As a result, any attempt to submit manipulated or before-run seeds will fail to produce either a counterexample or reward computation.

Moreover, some application may want to set up a time fame such that a parameter can only valid if this amout of time is passed. This grantee enough time for validators to valide the parameter. Then, the parameter is valid if and only if a certain amount of time having passed, no counterexample being found, and receiving enough computation proofs. 
\subsubsection{Reward manipulation attack}
In some applications, multiple computational proofs may be allowed. There are a record to monitor the progress of the parameter's verification. Namely, it includes the following details of the addresses of the validators and the random number $r$ used in the verification process. This record is crucial for preventing reward manipulation attack as a validator can not reclaim a new reward with the same random number.

The validators' addresses and the random number $r$ play a vital role in preventing reward-manipulation attacks. A validator cannot resubmit with the same $r$. Therefore, this uniqueness prevents validators from submitting the same computation proof or a counterexample multiple times.
\section{Gas Cost Analysis}
\label{sec:gas-cost-analysis}
This section evaluates the cost of the proposed distributed verification method and compares it to traditional on-chain verification.
\subsection{Transaction Execution Costs}
Transaction costs, measured in gas, can be divided into five key components:
\begin{enumerate}
\item Base cost: Fixed cost for initiating a transaction, covering operations like hashing, signature verification, and balance updates. For instance, transferring ETH in Ethereum costs 21,000 gas.
\item Data cost: Gas tied to the size of the transaction’s data payload, with non-zero bytes incurring higher costs than zero bytes.
\item Computational cost: Gas for executing smart contract operations, such as arithmetic, logic, control flow, cryptography, and memory tasks.
\item Storage cost: Higher than computation, as it involves writing to persistent storage. %In Ethereum, writing a new value costs 20,000 gas, updates cost 5,000 gas, and reading costs 100 gas.
\item Refund gas: Gas refunded for specific operations, like using SELFDESTRUCT or resetting storage values to zero.
\end{enumerate}
Thus, the total gas cost (execution cost) includes base, data, computational, and storage costs.
\subsection{Comparative Analysis of On-Chain and Offline Distributed Methods}
We can compare the gas costs of on-chain and off-chain verification by breaking down the components.
\subsubsection{On-chain verification gas costs}
Let \( G_{parameter} \) represent the intrinsic gas cost, which includes the base gas and data cost, primarily dependent on the size of the parameter \( p \). The total on-chain verification gas cost \( G_{on} \), as expressed in Equation \ref{on-gas}, consists of several parts:
\begin{itemize}
    \item The intrinsic gas \( G_{parameter} \),
    \item Optional storage gas \( G_{storage} \) (depending on whether the parameter is stored),
    \item Checking computation gas, which includes \( n \) checks of the parameter, each costing \( G_{check} \), where \( n \) is the size of the parameter,
    \item The gas for executing the actual work computation \( G_{run} \).
\end{itemize}
\begin{equation}
\label{on-gas}
G_{on} = G_{parameter} + [G_{storage}] + n \cdot G_{check} + G_{run}
\end{equation}
If the parameter is invalid, the gas for running the actual computation \( G_{run} \) is not required.
\subsubsection{Off-chain verification gas costs}
For our offline distributed verification method, we consider the gas costs associated with verifying the parameter and performing the actual work. The total cost includes the gas to :
\begin{itemize}
    \item submit the parameter, \( G_{parameter} \),
    \item store the parameter (or its hash), \( G_{storage} \),
    \item submit the seed, \( G_{seed} \),
    \item check the checkpoint corresponding to the seed, \( G_{check} \),
    \item compute the hash and compare it with the target hash, \( G_{hash} \),
    \item run the computation, \( G_{run} \), if the parameter is valid.
\end{itemize}
The total gas cost for the off-chain method is given by Equation \ref{gas-off}:
\begin{equation}
\label{gas-off}
G_{off} = G_{parameter} + G_{storage} + (G_{seed} + G_{check} + G_{hash}) + G_{run}
\end{equation}
\subsubsection{Comparative Analysis}
Let's compare the gas costs of both methods across different factors.

\paragraph*{Intrinsic Cost} Both methods incur the same intrinsic gas cost, \( G_{parameter} \).

\paragraph*{Storage Cost} The on-chain method has an optional storage cost \( [G_{storage}] \), while the offline method always includes \( G_{storage} \), although it may only store the parameter’s hash in some cases.

\paragraph*{Parameter Checking} In the on-chain method, the parameter check costs \( n \cdot G_{check} \), where \( n \) is the parameter size. In the offline method, this cost is reduced to \( G_{check} \).

\paragraph*{Additional Costs in the Offline Method} The offline method incurs additional costs for submitting seeds \( G_{seed} \) and computing/comparing hashes \( G_{hash} \), which the on-chain method does not require.

\paragraph*{Computation Costs} Both methods share the same computation cost, \( G_{run} \).

Let \( G_{base} \) represent the sum of the gas costs for submitting, storing, and running the parameter:

\[
G_{base} = G_{parameter} + [G_{storage}] + G_{run}
\]

Since centralized verification only incurs gas costs, while the distributed process uses a proof-of-work incentive, we convert the reward into gas terms. Let \( G_{reward} \) denote the gas equivalent of the reward for finding a counterexample or computation proof. Let \( G_{proof} \) represent the total gas cost to perform and reward the computation proof:

\[
G_{proof} = G_{seed} + G_{check} + G_{hash} + G_{reward}
\]

If the base gas does not include storage gas, then \( G_{proof} \) will factor it in.

>>>>

\lstdefinelanguage{solidity}{
  backgroundcolor=\color{pink!20},
  keywords={contract, function, public, int},
  keywordstyle=\bfseries\color{blue},
  commentstyle=\itshape\color{green!40!black},
  basicstyle=\ttfamily,
  morecomment=[l]{//},
  morecomment=[s]{/*}{*/},
  morestring=[b]",
  sensitive=true
}
\begin{document}
%
\title{Gas-Efficient Parameter Verification for Blockchain Smart Contracts Using Off-Chain Validators}
%
\titlerunning{Off-Chain Parameter Verification Approach: Gas-Efficient}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Thi Thu Ha Doan\orcidID{0000-0001-7524-4497}\and Peter Thiemann\orcidID{0000-0002-9000-1239}}
%
\authorrunning{Ha Doan, P. Thiemann}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of Freiburg, Germany \\
  \email{\{doanha,thiemann\}@informatik.uni-freiburg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
In certain blockchain scenarios, verifying the properties of parameters may require significant gas costs or be infeasible due to gas limits. This study proposes a distributed verification protocol to address these challenges. The core concept involves offloading the verification process to validators, who attempt to find counterexamples or proofs off-chain. If a counterexample is discovered, it can be submitted for re-verification on-chain. If validated, the parameter is discarded; otherwise, the correctness of the parameter is guaranteed through a proof-of-work incentive mechanism, encouraging validators to participate in the distributed verification process. To implement these ideas, we propose a practical model that also tackles potential security concerns. We developed a prototype of the protocol and conducted a cost analysis, demonstrating its gas efficiency and practical utility.
\keywords{blockchain, off-chain verification, gas optimization, proof-of-work, distributed verification}
\end{abstract}
%
%
%
\section{Introduction}
\label{sec:introduction}
\lstset{language=solidity}
A smart contract is a critical component of blockchain technology, with applications ranging from simple tasks like auctions to more complex systems such as decentralized markets. However, broader adoption of smart contracts faces challenges, with gas costs being among the most significant. Every computation performed by a smart contract on the blockchain incurs a cost, as each unit of computation and storage consumed by an algorithm must be paid for due to the burden it places on the system \cite{eth-whitepaper,yellowpaper}.

@@

\begin{lstlisting}[numbers=none]
contract Sorted {
  function find (int[100] a, int v) public {
    // assume a is sorted 
  ... } 
}
\end{lstlisting}
The explicit assertion would be:
\begin{gather*}\label{}
  (\forall k) (0\leq k <99) \Rightarrow a[k] \leq a[k+1]
\end{gather*}
This check can be performed in \(O(1)\) time, but the associated constant factor makes it costly.

@@

The paper is structured as follows: The next section defines the parameter verification problems and presents use cases. Section \ref{sec:offchain-distributed-verification-approach} proposes the novel approach, while Section \ref{sec:practical-model} introduces its practical model. Section \ref{sec:gas-cost-analysis} analyzes the gas costs, comparing our proposed approach with the on-chain method. Section \ref{sec:prototype-implementation} details the prototype implementation. Section \ref{sec:related-work} discusses related work, and Section \ref{sec:conclusion} concludes the paper.
\section{Parameter Assertion Verification On-chain}
\label{sec:parameter-assertion-verification-onchain}
Our work focuses on parameters that are computationally expensive to verify on-chain. Specifically, we address cases where verifying a parameter assertion requires loops within the contract and the assertion can be formalized using universal or existential quantifiers.
\subsection{Parameter Assertion Formalization}
\paragraph{Universal Quantifier Formalization}
An assertion can be formalized using the universal quantifier as follows:
\begin{gather}
  \label{eq:1}
  \forall a \in A. \, P(a)
\end{gather}
This formula can be extended to assertions over multiple domains as:
\begin{gather}
  \label{eq:2}
  \forall a \in A, \, \forall b \in B, \, \dots \, P(a, b, \dots)
\end{gather}
\paragraph{Existential Quantifier Formalization}
In cases where an assertion involves the existence of an element, it can be formalized using existential quantifiers as follows:
\begin{gather}
  \label{eq:3}
  \exists a \in A. \, P(a)
\end{gather}
This formula can also be extended to assertions over multiple domains:
\begin{gather}
  \label{eq:4}
  \exists a \in A, \, \exists b \in B, \, \dots \, P(a, b, \dots)
\end{gather}
\subsection{On-chain Verification}
Verifying these assertions on-chain requires iterating over the domain \(A\) within the contract. For the fomulas \ref{eq:5}, the verification fomulas is as follows.
\begin{gather}
  \label{eq:5}
  \bigwedge_{a \in A} P(a)
\end{gather}
For multiple domains, the verification process becomes:
\begin{gather}
  \label{eq:6}
  \bigwedge_{a \in A, b \in B, \dots} \dots P(a, b, \dots)
\end{gather}
Verifying these assertions in  the existential quantifier formalization requires iterating over the domain \(A\) until finding an element \(a\) that satisfies the predicate:
\begin{gather}
  \label{eq:7}
  \bigvee_{a \in A} P(a)
\end{gather}

@@

\paragraph{\textbf{Numbers}}

@@

\paragraph{\textbf{Booleans}}

@@

\paragraph{\textbf{Strings}}

@@

\paragraph{\textbf{Bytes}}

@@

\paragraph{\textbf{Arrays (or Lists)}}

@@

\paragraph{\textbf{Sets}}

@@

To determine the number of seeds needed based on the expected probability of detecting a problem, we define \( p \) as the expected probability of finding at least one counterexample. 
\begin{itemize}
    \item The probability of a single seed failing to find a counterexample is \( \frac{n-1}{n} \).
    \item The probability of all \( m \) seeds failing is \( \left( \frac{n-1}{n} \right)^m \).
    \item Thus, the probability of at least one seed finding a counterexample is:
\begin{gather*}
  p = 1 - \left( \frac{n-1}{n} \right)^m
\end{gather*}
\end{itemize}
%Rearranging this gives:
%\begin{gather*}
%\left( \frac{n-1}{n} \right)^m = 1 - p
%\end{gather*}
%Taking the natural logarithm:
%\begin{gather*}
%m \ln\left( \frac{n-1}{n} \right) = \ln(1 - p)
%\end{gather*}
Solving for \( m \):
\begin{gather}
\label{eq:12}
m = \frac{\ln(1 - p)}{\ln\left( \frac{n-1}{n} \right)}
\end{gather}

@@

\begin{enumerate}
\item Denial-of-service (DoS) attacks: The system is susceptible to DoS attacks, where a caller inundates the system with numerous invalid parameters, causing congestion and hindering its operation.
\item Front-running attacks: The system is vulnerable to front-running attacks, where an attacker closely monitors the mempool to intercept a seed representing a counterexample or a computation proof, subsequently stealing the reward.
\item Caller exploitation: A caller might exploit the system by running the negation check privately to (1) identify the reward before submitting the parameter on-chain, thereby swiftly claiming the reward ahead of the other validators, (2) fake the compuatation proofs before a counterexample can be found by other validators.
\item Reward manipulation: For a system that allows multiple rewards. A validator may attempt to manipulate the reward system by resubmitting counterexamples or computation proofs multiple times to multiply their rewards.
\end{enumerate}
\subsection{Overview architect}
This section presents a practical model that unifies theoretical principles and addresses the previously mentioned security concerns. The architectural design of this model is depicted in Figure \ref{fig.architect}.  
\subsubsection{Main compoments.} The model consists of two main entities: the on-chain assertion contract and the off-chain validator program.
\paragraph{On-chain assertion contract.}
While additional functions may exist, the assertion contract must encompass the following two essential functions (or similar functions):
\begin{itemize}
\item The \( submitParameter \) function: Callers utilize this function to submit their parameters for validation. %Subsequently, the parameter is distributedly verified by validators.
\item  The \( claimReward \) function: This function accepts a seed (or may some others) as inputs, yielding a result indicating whether the computation from the seed results in a counterexample, a reward computation, or a non-reward computation.
\end{itemize}
\paragraph{Off-chain validator program.}
Since the off-chain program runs off-chain, it can be implemented according to the validator's preferences. However, the crucial point is that the off-chain contract must use the exact same \( claimReward \) function when attempting to find a counterexample or a computation proof. Additionally, it should support a function that assists the validator in finding a seed to earn a reward.

All events such as parameter submissions, the discovery of a counterexample, or the presentation of computational proofs can be broadcasted to the network using event emission. Validators can monitor these events to stay updated on the verification status in real-time.
\paragraph{Storage.}
When a parameter is submitted for verification, the following information should be stored:
\begin{itemize}
\item Parameter: this includes the parameter itself. In cases where storing the parameter on-chain is impractical because of its size, it could be possible to store only its hash. Despite this, the hash remains sufficient for validation.
\item Timestamp: this indicates the approximate time when the parameter was submitted.
\end{itemize}
\begin{figure}
\centering
\includegraphics[scale=.8]{assertion1}
\caption{The architecture of the practical model}
\label{fig.architect}
\end{figure}
\subsubsection{Deploying and managing on/off-chain contracts.}
The respective owner is responsible for deploying the on-chain contract and ensuring that the off-chain program is accessible to validators. There are two approaches to make the program available to validators:
\begin{itemize}
   \item The owner may store the program code in a repository that is accessible to validators or provide it directly to them upon request. 	\item Alternatively, the owner can broadcast the program to the network using messaging systems like Waku in Ethereum, allowing interested validators to store the off-chain code locally.
\end{itemize}

%\subsubsection{On and Off.} 
%Before a parameter can be utilized in the actual work function or contract, a caller must initially submit it via the submit-parameter function in the on-chain assertion contract.

%Upon the submission of a parameter, an event can be emitted, allowing validators to receive updates by monitoring the blockchain for the parameter submission event. Additionally, the caller may choose to broadcast their parameter to all validators via a messaging system when submitting it online.
%\subsubsection{Off-chain verification}
%After a parameter is submitted and stored on-chain, a validator can commence the verification process. To assess the validity of a parameter, each validator independently executes the off-chain validation program.

%A validator may attempt to try multiple times with different random seeds in order to find either a counterexample or a computational proof. A function called find-seed could be implemented, which in turn calls the claim-reward function to locate a seed.

%All events such as parameter submissions, the discovery of a counterexample, or the presentation of computational proofs can be broadcasted to the network using event emission. Validators can monitor these events to stay updated on the verification status in real-time. 
\subsubsection{Calling a work function}
A work function can be encapsulated as a private function within the assertion contract or implemented in a separate contract. A caller submits a parameter for verification through the on-chain assertion contract. Once verified, the work contract is triggered to perform its task under the assumption that the parameter is valid.

The work function or contract is invoked by the on-chain validation contract or caller, but only if specific conditions are met, such as sufficient verification proofs, no counterexamples, and a waiting period. Upon fulfilling all requirements, the task is executed, and in some cases, the parameter record may be deleted to free up storage.
\subsection{Security Features}
\subsubsection{DoS attacks}
When submitting a parameter, the caller must provide a deposit in native tokens. This deposit is claimed by a validator if a counterexample is found or returned if the parameter is verified. The deposit discourages invalid submissions and mitigates the risk of DoS attacks.
\subsubsection{Front-running attacks}
To prevent front-running attacks, the seed \( s \) is calculated by combining a random number \( r \) with the validator's address, rather than using \( r \) alone. This approach enhances security, as a malicious validator cannot reuse \( r \) from the mempool - its combination with their own address will yield a different seed \( s \).

%While a random number $r$ alone as a seed is sufficient to indicate the associated element $a$ in the domain $A$, to prevent the front-running attack, we enhance the randomness of the seed by combining a random number with the validator's address to calculate the seed.

%This combination adds an extra level of security. So even watching the mempool and get the random number, a malicious validators cannot use the same random number $r$  because the combination with their address will not produce the same seed $s$.

 %In deeds, the validator's address is converted to numerical values and use these numbers in combination with a random number to compute the seed.

%Let's denote the validator's address by $addr$: \(\quad \text{addr} \in \text{Addresses}\)

%The address is converted to numerical values.
%\begin{equation}
%\text{addr\_num} = \text{init256}(\text{addr})
%\end{equation}

%This combination adds an extra level of security. So even watching the mempool and get the random number, a malicious validators cannot use the same random number $r$  because the combination with their address will not produce the same seed $s$.
\subsubsection{Caller exploitation attack}
%A caller may execute the validator program for their parameters before submitting on-chain, attempting to claim a reward or validate their parameter before others find counterexamples.
To mitigate the caller exploitation risk, the seed \( s \) is computed using the block timestamp \( t \) indicating when the parameter is submitted, random number \( r \), and validator's address. The timestamp \( t \in \text{Timestamps} \) is included to prevent preemptive submission, and the seed \( s \) is calculated as:
\begin{equation}
s = \text{hash}(r, \text{addr}, t)
\end{equation}
where \(\text{hash}\) is a cryptographic hash function. This ensures that manipulated or pre-run seeds fail to produce counterexamples or rewards.
%Additionally, applications can enforce a time frame such that a parameter is valid only if enough time has passed for verification. A parameter is valid if, after this time, no counterexample is found and sufficient computation proofs are received.
\subsubsection{Reward manipulation attack}
In some applications, multiple computational proofs are allowed, and a record is maintained to track the parameter's verification progress. This record contains validator addresses and the random number \( r \) used in each verification.

The inclusion of validators' addresses and \( r \) is crucial in preventing reward manipulation, as it ensures that a validator cannot resubmit with the same \( r \), thereby preventing repeated claims for the same computation proof or counterexample.
\section{Gas Cost Analysis}
\label{sec:gas-cost-analysis}
This section evaluates the cost of the proposed distributed verification method and compares it to traditional on-chain verification.
\subsection{Transaction Execution Costs}
Transaction costs, measured in gas, can be divided into five key components:
\begin{enumerate}
\item Base cost: Fixed cost for initiating a transaction, covering operations like hashing, signature verification, and balance updates. For instance, transferring ETH in Ethereum costs 21,000 gas.
\item Data cost: Gas tied to the size of the transaction’s data payload, with non-zero bytes incurring higher costs than zero bytes.
\item Computational cost: Gas for executing smart contract operations, such as arithmetic, logic, control flow, cryptography, and memory tasks.
\item Storage cost: Higher than computation, as it involves writing to persistent storage. %In Ethereum, writing a new value costs 20,000 gas, updates cost 5,000 gas, and reading costs 100 gas.
\item Refund gas: Gas refunded for specific operations, like using SELFDESTRUCT or resetting storage values to zero.
\end{enumerate}
Thus, the total gas cost (execution cost) includes base, data, computational, and storage costs.
\subsection{Comparative Analysis of On-Chain and Offline Distributed Methods}
We compare the gas costs of on-chain and off-chain verification by breaking down their components.
\subsubsection{On-chain Verification Gas Costs}
Let \( G_{parameter} \) represent the intrinsic gas cost, which includes base and data costs, primarily depending on the size of the parameter \( p \). The total on-chain gas cost \( G_{on} \), given in Equation \ref{on-gas}, includes:
\begin{itemize}
    \item Intrinsic gas \( G_{parameter} \),
    \item Optional storage gas \( G_{storage} \),
    \item Gas for \( n \) parameter checks, each costing \( G_{check} \),
    \item Execution gas \( G_{run} \), if the parameter is valid.
\end{itemize}
\begin{equation}
\label{on-gas}
G_{on} = G_{parameter} + [G_{storage}] + n \cdot G_{check} + G_{run}
\end{equation}

\subsubsection{Off-chain Verification Gas Costs}
The off-chain verification gas costs include similar components to on-chain verification but differ in several key aspects. Instead of \( n \) parameter checks, only a single check is required. Moreover, storage cost \( G_{storage} \) is mandatory, and additional components are needed as follows:
\begin{itemize}
    \item Submit the seed, \( G_{seed} \),
    \item Compute and compare the hash, \( G_{hash} \).
\end{itemize}
The total off-chain gas cost is given by Equation \ref{gas-off}:
\begin{equation}
\label{gas-off}
G_{off} = G_{parameter} + G_{storage} + (G_{seed} + G_{check} + G_{hash}) + G_{run}
\end{equation}

\subsubsection{Comparative Analysis}
We compare the gas costs of both verification methods.

\paragraph*{Intrinsic Cost} Both methods incur the same intrinsic cost, \( G_{parameter} \).

\paragraph*{Storage Cost} On-chain storage cost \( [G_{storage}] \) is optional, whereas the offline method always includes \( G_{storage} \), which may store only the parameter's hash.

\paragraph*{Parameter Checking} The on-chain method incurs \( n \cdot G_{check} \) for parameter checking, while the offline method reduces this to \( G_{check} \).

\paragraph*{Additional Costs} The offline method includes costs for seed submission \( G_{seed} \) and hash computation \( G_{hash} \), which are not required on-chain.

\paragraph*{Computation Costs} Both methods share the computation cost, \( G_{run} \).

Define \( G_{base} \) as the sum of submission, storage, and computation costs:
\[
G_{base} = G_{parameter} + [G_{storage}] + G_{run}
\]

The offline distributed process uses a proof-of-work incentive; let \( G_{reward} \) be the gas equivalent reward for counterexamples or proofs. The total verification cost for proof \( G_{proof} \) is:
\[
G_{proof} = G_{seed} + G_{check} + G_{hash} + G_{reward}
\]

Figure \ref{fig:gas_compare} compares gas consumption between methods, with \( G_{base} \) assumed constant. The red line (on-chain) scales linearly with parameter size \( n \), while the blue line (offline) initially incurs higher costs but becomes more efficient as \( n \) grows.

The on-chain method is best for scenarios requiring direct blockchain checks, but it becomes costly when \( n \) and \( G_{check} \) are large. The proposed offline method (\( G_{off} \)) is more efficient for large parameters, despite additional \( G_{seed} \) and \( G_{hash} \) costs, which are often outweighed by savings in reduced checks.

For the offline method, the main concern is \( G_{storage} \). If storing the parameter is required, this cost is negligible, but if not, it must be considered, potentially storing only the parameter's hash for verification.
